### 2022-02-14 introduction/introduction.tex
more

Since its introduction, resolution was improved in many ways. Strategies and
heuristics~\cite{lw-65-sos} to curb the explosion of the search space were
introduced, as well as complete, but less explosive variants of the calculus \cite{cc-73-resolution-book}. Despite this
progress, reasoning about equality of objects was still hard for these methods. This changed with introduction of
superposition in 199

>>>>

Since its introduction, resolution was improved in many ways. Strategies and
heuristics~\cite{lw-65-sos} to curb the explosion of the search space were
introduced, as well as complete, but less explosive variants of the calculus
\cite{cc-73-resolution-book}. Despite this progress, reasoning about equality of
objects was still hard for these methods. This changed with introduction of
superposition \cite{bg-94-superposition} in early 1990s.

Superposition is a complete calculus for first-order logic loosely based on
resolution, featuring support for equality on the calculus level. This support
is further optimized by use of term orders and selection functions to prune the
search space. Thanks to efficient implementation, this calculus was used to
prove long-standing open problem known as ``Robbins conjecture''
\cite{mccune-97-robbins}. Furthermore, provers based on this calculus have been
winning the first-order division of CASC theorem proving competition since its
inception in the 1990s \cite{ss-96-casc}.

Even though the successes such proving Robbins conjecture show that it is
possible, automatically proving hard mathematical problems is still out of reach
for theorem provers. However, computers can still be used to verify human-written proofs.
